# Differential analysis

Parameters used for the differential analysis :

* Design : `r params$listAnaDiff$design` 
* method : `r params$listAnaDiff$method`
* t-test : `r params$listAnaDiff$ttest_options`
* Threshold logFC = `r params$listAnaDiff$th_logFC`
* All pairwise comparison names = `r params$listAnaDiff$AllPairwiseCompNames`
* Comparison = `r params$listAnaDiff$comp`
* Threshold p-value : `r params$listAnaDiff$th_pval`
* Calibration method = `r params$listAnaDiff$calibMethod`
* FDR = `r round(params$listAnaDiff$fdr, 2)` %
* Swap volcano plot = `r params$listAnaDiff$swapVolcano`
* Filter type : `r params$listAnaDiff$filterType`
* Filter th NA = `r params$listAnaDiff$filter_th_NA`
* Numerical value calibration method = `r params$listAnaDiff$numValCalibMethod`                                                   
                                                       
                                                       
```{r fig_logFC_dist,out.width = "50%", echo=FALSE}
knitr::include_graphics(paste(tempdir(), sessionID, gGraphicsFilenames$logFC_Distribution, sep="/"))
```


```{r fig_calibrationALL,out.width = "100%", echo=FALSE}
knitr::include_graphics(paste(tempdir(), sessionID, gGraphicsFilenames$calibrationPlotAll, sep="/"))
```

```{r fig_calibration,out.width = "50%", echo=FALSE}
#knitr::include_graphics(paste(tempdir(), sessionID, gGraphicsFilenames$calibrationPlot, sep="/"))
```


```{r fig_volcano,out.width = "100%", echo=FALSE}
knitr::include_graphics(paste(tempdir(), sessionID, gGraphicsFilenames$volcanoPlot_3, sep="/"))
```

