# Normalization
           
Parameters used for the normalization step :

* Normalization method : `r params$listNormalization$method`
* Normalization type : `r params$listNormalization$type`
* Normalization quantile = `r params$listNormalization$quantile`
* Normalization scaling : `r params$listNormalization$varReduction`
* Normalization spanLOESS : `r params$listNormalization$spanLOESS`
 
                                                            
                                                             
```{r fig_boxplotNorm,out.width = "100%", echo=FALSE}
knitr::include_graphics(normalizePath(paste(tempdir(), gGraphicsFilenames$boxplotAfterNorm, sep="/")))
```

```{r fig_densityplotNorm,out.width = "75%", echo=FALSE}
knitr::include_graphics(normalizePath(paste(tempdir(), gGraphicsFilenames$densityPlotAfterNorm, sep="/")))
```

```{r fig_compNorm,out.width = "100%", echo=FALSE}
knitr::include_graphics(normalizePath(paste(tempdir(), gGraphicsFilenames$compareNorm, sep="/")))
```

