# Normalization
           
Parameters used for the normalization step :

* Normalization method : `r params$listNormalization$method`
* Normalization type : `r params$listNormalization$type`
* Normalization quantile = `r params$listNormalization$quantile`
* Normalization quantileOther = `r params$listNormalization$quantileOther`
* Normalization scaling : `r params$listNormalization$scaling`
                                                             
                                                             
                                                             
```{r fig_boxplotNorm,out.width = "100%", echo=FALSE}
knitr::include_graphics(paste(tempdir(), sessionID, gGraphicsFilenames$boxplotAfterNorm, sep="/"))
```

```{r fig_densityplotNorm,out.width = "75%", echo=FALSE}
knitr::include_graphics(paste(tempdir(), sessionID, gGraphicsFilenames$densityPlotAfterNorm, sep="/"))
```

```{r fig_compNorm,out.width = "100%", echo=FALSE}
knitr::include_graphics(paste(tempdir(), sessionID, gGraphicsFilenames$compareNorm, sep="/"))
```

